Predicting Diabetes Based on Various Factors Using logistic Regression

### 2023-11-13 manuscript/manuscript.tex
minor edits
Addition of VIF table and beginning of assumption section

@@

\section{Methods}
\label{sec:meth}
    Various methods will be used to complete the statistical analysis necessary for this project. I will begin by exploring basic descriptive statistics to gain an understanding of my data set. I will then progress to creating visualizations including histograms and box plots to understand relationships and patterns within my data. In order to draw insight on my data I will perform logistic regression analysis to determine which predictors are significant in predicting if someone has diabetes. Within this analysis I will perform necessary transformations in order to create the best model that I can. From my results I will draw necessary conclusions about my data.

>>>>

The rest of the paper is organized as follows.
The data will be presented in Section~\ref{sec:data}.
The methods are described in Section~\ref{sec:meth}.
The results are reported in Section~\ref{sec:resu}.
A discussion concludes in Section~\ref{sec:disc}.

@@

\section{Methods}
\label{sec:meth}
    Various methods will be used to complete the statistical analysis necessary for this project. I will begin by exploring basic descriptive statistics to gain an understanding of my data set. I will then progress to creating visualizations including histograms and box plots to understand relationships and patterns within my data. In order to draw insight on my data I will perform logistic regression analysis to determine which predictors are significant in predicting if someone has diabetes. In order to perform the logistic regression, I will have to check the necessary assumptions associated with the method. Within this analysis I will perform necessary transformations in order to create the best model that I can. From my results I will draw necessary conclusions about my data.

    The first assumption that will be checked in that the dependent variable is binary, this true as our outcome variable is in the form of 1 (having diabetes) or 2 (not having diabetes). The next assumption that will be checked is if the observations are independent of each other, this is also true for our data as each predictor is calculated or taken independent of one another. The third assumption that will be checked is that there is no multicollinearity among the independent variables. In order to check this assumption we will calculate the variance inflation factor, VIF, in order to measure the strength of the correlation between predictor variables in our model. One example of this is seen in Table~\ref{tab:vif} where all of the values are around 1, indicating that there is moderate correlation between pregnancies and the other predictors but this value is not in a concerning range.

\begin{table}[ht]
\caption{VIF Values} 
\label{tab:vif}
\centering
\begin{tabular}{rr}
  \hline
 & vif(lm(P \~{} G + BP + ST + I + BMI + DPF + A)) \\ 
  \hline
Glucose & 1.29 \\ 
  BloodPressure & 1.18 \\ 
  SkinThickness & 1.50 \\ 
  Insulin & 1.44 \\ 
  BMI & 1.30 \\ 
  DiabetesPedigreeFunction & 1.06 \\ 
  Age & 1.18 \\ 
   \hline
\end{tabular}
\end{table}
